\documentclass[oneside,11pt]{book}

\usepackage{graphicx}

\usepackage{epstopdf}
\usepackage{epsfig}

\usepackage{float}
\usepackage{amssymb,amsmath}
\newcommand{\bm}[1]{\boldsymbol{#1}}

\usepackage[makeroom]{cancel} %for cancel out in eq.

\usepackage{multirow}
\usepackage{fullpage}
\usepackage[titletoc,title]{appendix}
\usepackage{setspace}

\usepackage[bf, small, center]{caption}
\setlength{\belowcaptionskip}{10pt}

\usepackage{longtable}

\usepackage{geometry} % for page margin for odd and even pages to bind them
\geometry{
% top=1.0in,  
 inner=3.5cm,
 outer=1.0in,
  bottom=1.2in,
%  headheight=3ex, 
  headsep=3ex,         
}

% \doublespacing
\onehalfspacing


\usepackage{fancyhdr} % for the header
\pagestyle{fancy}
\fancyhead[L]{\it \leftmark}
\fancyhead[R]{\thepage}
\fancyfoot[]{}
% \renewcommand{\headrulewidth}{0.3pt}

\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}



\usepackage[phd]{thesisfrontmatter}

% *** NOTE WHICH PROGRAM GENERATED IMAGES OR WHICH POWER POINT THEY ARE FROM
%compare methodology with script for final process
%how much detail in methodology?
%some sort of processing flowchart?
%how much do we care about processing?

\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent


\usepackage{mathtools}


\usepackage{color}
\usepackage{soul}



\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\let\stdsection\chapter  
\renewcommand\chapter{\newpage\stdsection}  

%%%%%%%%%%% for Appendix
% \makeatletter
% \newcommand\appendix@section[1]{%
%   \refstepcounter{section}%
%   \orig@section*{Appendix \@Alph\c@section: #1}%
%   \addcontentsline{toc}{section}{Appendix \@Alph\c@section: #1}%
% }
% \let\orig@section\section
% \g@addto@macro\appendix{\let\section\appendix@section}
% \makeatother



% Added 09-24-15 ----------------------------------------
\usepackage{breakcites}



% Added 11-12-13 ----------------------------------------

\usepackage{titlesec} % For the spacing after and before chapter title

\titleformat{\chapter}[display]
    {\normalfont\huge\bfseries}{\chaptertitlename \thechapter}{10pt}{\Huge}
\titlespacing*{\chapter}{0pt}{40pt}{20pt}

\titlespacing*{\section}{0ex}{2.5ex}{2ex}
\titlespacing*{\subsection}{0ex}{1.5ex}{1ex}

% Added 09-21-15 ----------------------------------------
%Options: Sonny, Lenny, Glenn, Conny, Rejne, Bjarne, Bjornstrup
\usepackage[Bjornstrup]{fncychap}
\ChTitleVar{\raggedleft\Huge\rmfamily\bfseries}
% ----------------------------------------

\usepackage{indentfirst}
\setlength{\parindent}{20pt}

% Added 11-17-13 ----------------------------------------
% Select what to do with todonotes: 
\usepackage[disable]{todonotes} % notes not showed
% \usepackage[draft]{todonotes}   % notes showed
\setlength{\marginparwidth}{2cm}

\usepackage{tikz} % for flow charts
  \usetikzlibrary{shapes,shapes.geometric,arrows,positioning,shadows,calc}


\begingroup\newif\ifmy
\IfFileExists{linereg.data}{}{\mytrue}
\ifmy
\begin{filecontents}{linereg.data}
#x y
0 4
10 24
\end{filecontents}
\fi\endgroup

\begingroup\newif\ifmy
\IfFileExists{linereg2.data}{}{\mytrue}
\ifmy
\begin{filecontents}{linereg2.data}
#x y
2 8
8 20
\end{filecontents}
\fi\endgroup

\usepackage{colortbl}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{multirow}

\listfiles

\setlength{\headheight}{15pt} % to avoid "Package Fancyhdr Warning: \headheight is too small (0.0pt): Make it at least 12.0pt."

% Added 02-18-14 ----------------------------------------
% \setlength{\abovecaptionskip}{-2ex}
% \setlength{\belowcaptionskip}{-4ex} % space after caption
%******************************************************************************************************

% Added 08-10-14 
\usepackage{enumitem}

% Added 07-28-15 
\usepackage[percent]{overpic}
\usepackage{morefloats} % for the error "Too many unprocessed floats"

% -------------------------------------------------------

% Added 09-28-15 ----------------------------------------
% Load the package with the acronym option
\usepackage[acronym,nomain,toc,ucmark=true]{glossaries}
% Generate the glossary
\makeglossaries
\renewcommand*{\acronymname}{Acronyms and Abbreviations}
\include{Acronyms} % to include Acronyms.tex

% Added 11-15-13 ----------------------------------------
\includeonly{Acronyms,Introduction,Objectives,Background_and_Theory,Methodology,Results,Summary,Appendix,Vita} 
% \includeonly{Acronyms,Introduction,Results}

% Added 10-21-15 ----------------------------------------
\usepackage{pdflscape}

% Added 10-22-15 ----------------------------------------
\usepackage{seqsplit}

% Added 10-23-15 ----------------------------------------
\usepackage{tocbibind}
% ----------------------------------------
\usepackage{seqsplit}
\usepackage{hyperref}
\hypersetup{
    % bookmarks=true,         % show bookmarks bar?
    unicode=false,          % non-Latin characters in AcrobatÕs bookmarks
    pdftoolbar=true,        % show AcrobatÕs toolbar?
    pdfmenubar=true,        % show AcrobatÕs menu?
    pdffitwindow=false,     % window fit to page when opened
    pdfstartview={FitH},    % fits the width of the page to the window
    pdftitle={L8's potential for water constituents retrieval },    % title
    pdfauthor={Javier Concha},     % author
    pdfsubject={Subject},   % subject of the document
    pdfcreator={Creator},   % creator of the document
    pdfproducer={Producer}, % producer of the document
    pdfkeywords={keyword1} {key2} {key3}, % list of keywords
    pdfnewwindow=true,      % links in new window
    colorlinks=true,       % false: boxed links; true: colored links
    % linkcolor=blue,          % color of internal links
    % citecolor=cyan,        % color of links to bibliography
    % filecolor=magenta,      % color of file links
    % urlcolor=blue,           % color of external links
    linkcolor=black,          % color of internal links
    citecolor=black,        % color of links to bibliography
    filecolor=black,      % color of file links
    urlcolor=black,           % color of external links
    breaklinks=true
}

\usepackage[all]{hypcap} % to see figure with hyper ref

\setcounter{secnumdepth}{5}
\setcounter{tocdepth}{5}

% Added 12-03-13 ----------------------------------------
\usepackage{imakeidx} % to create index
\indexsetup{othercode=\small}
\makeindex[program=makeindex,columns=2,intoc=true,options={-s MyIndex.ist}]
% \usepackage{imakeidx}     % use this one when is not working
% \makeindex                % use this one when is not working

% Added 10-25-15 ----------------------------------------
\usepackage{silence}
\WarningFilter{latex}{Text page}
\WarningFilter{latex}{Float too large}
\WarningFilter{latex}{Marginpar on page}

% Added 10-26-15 ----------------------------------------
\usepackage{listings}
\usepackage{xcolor} 

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
 
\lstset{ %
  % language=Matlab,                % the language of the code
  basicstyle=\small\ttfamily\color{black},           % the size of the fonts that are used for the code
  numbers=left,                   % where to put the line-numbers
  numberstyle=\tiny\color{gray},  % the style that is used for the line-numbers
  stepnumber=2,                   % the step between two line-numbers. If it's 1, each line 
                                  % will be numbered
  numbersep=5pt,                  % how far the line-numbers are from the code
  backgroundcolor=\color{white},      % choose the background color. You must add \usepackage{color}
  showspaces=false,               % show spaces adding particular underscores
  showstringspaces=false,         % underline spaces within strings
  showtabs=false,                 % show tabs within strings adding particular underscores
  frame=single,                   % adds a frame around the code
  rulecolor=\color{black},        % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. commens (green here))
  %tabsize=2,                      % sets default tabsize to 2 spaces
  captionpos=b,                   % sets the caption-position to bottom
  breaklines=true,                % sets automatic line breaking
  breakatwhitespace=false,        % sets if automatic breaks should only happen at whitespace
  title=\lstname,                   % show the filename of files included with \lstinputlisting;
                                  % also try caption instead of title
  keywordstyle=\color{black},          % keyword style
  commentstyle=\color{black},       % comment style
  stringstyle=\color{black},         % string literal style
  escapeinside={\%*}{*)},            % if you want to add a comment within your code
  morekeywords={*,...,lsqnonlin},              % if you want to add more keywords to the set
  aboveskip=10pt,
  belowskip=-12pt
}

% Added 11-05-15 ----------------------------------------
\usepackage[round]{natbib} 
% from
% http://tex.stackexchange.com/questions/117428/get-round-brackets-with-apalike
% o your preamble. For regular in text citations, use

% \citet{<key>} % or \cite{<key>}
% and for citations enclosed in parentheses use

% \citep{<key>}
%%%%%%%%%%%%%%
%******************************************************************************************************
%******************************************************************************************************
%******************************************************************************************************
\begin{document}

\degreetitle{The Use of Landsat 8 for Monitoring of \\Fresh and Coastal Waters}
\degreeauthor{Javier A. Concha}
% \degreedate{November 18, 2015}
\degreedate{\today{}}
\prevdegreeA{B.S. Electronics Engineering, Universidad de Concepci\'on, Chile, 2008}
\prevdegreeB{M.S. Imaging Science, Rochester Institute of Technology, NY, USA, 2012}
\advisor{Dr. John R. Schott}
\memberA{Dr. Anthony Vodacek}
\memberB{Dr. Charles Bachmann}
\memberC{Dr. Christy Tyler}
% \memberD{Dr. Christy Tyler}

% \pagenumbering{gobble} % no page number displayed
\pagenumbering{roman}

\makedeclaration

\makePHDproposalapproval

% \makecopyright

% \maketitle

% \chapter*{Abstract}
% \addcontentsline{toc}{chapter}{Abstract}


\begin{abstract}
\phantomsection
\addcontentsline{toc}{chapter}{Abstract}


\setlength{\parindent}{20pt}
% 300 Words max.
% Background/motivation/context
The most interaction between humankind and water occurs in coastal and inland waters (Case 2 waters) at a scale of tens or hundred of meters, but there is not yet an ocean color product (e.g. chlorophyll-{\it a} product) at this spatial scale.
%
Landsat 8 could potentially address the remote sensing of these kinds of waters due to its improved features. 
% Aim/objectives(s)/problem statement
This work presents an approach to obtain the color producing agents (CPAs) chlorophyll-{\it a}, colored dissolved organic material (CDOM) and suspended material (SM) from water bodies using Landsat 8.
%
Adequate atmospheric correction becomes an important first step to accurately retrieving water parameters since the sensor-reaching signal due to water is very small when compared to the signal due to the atmospheric effects. 
% Methods
We developed the model-based empirical line method (MoB-ELM) atmospheric correction method. 
%
The Mob-ELM employs pseudo invariant feature (PIF) pixels extracted from a reflectance product along with the in-water radiative transfer model HydroLight. 
%
We used a look-up-table-based (LUT-based) inversion methodology to simultaneously retrieve CPAs.
%
The LUT of remote-sensing reflectance spectra was created in Hydrolight using inherent optical properties (IOPs) measured in the field.

% Results
The retrieval algorithm was applied over three Landsat 8 scenes.
%
The CPA concentration maps exhibit expected trends of low concentrations in clear waters and higher concentrations in turbid waters. 
%
We estimated a normalized root mean squared error (NRMSE) of about $14\%$ for Chlorophyll-{\it a}, $11\%$ for the total suspended solid (TSS), and $7\%$ for colored dissolved organic matter (CDOM) when compared with {\it in situ} data. 
% Conclusions
These results demonstrate that the developed algorithm allows the simultaneous mapping of concentration of all CPAs in Case 2 waters and over areas where the standard algorithms are not available due to spatial resolution.
%
Therefore, this study shows that the Landsat 8 satellite can be utilized over Case 2 waters as long as a careful atmospheric correction is applied and IOPs are known. 

% Background/motivation/context
% Aim/objectives(s)/problem statement
% Approach/method(s)/procedure(s)/materials
% Results
% Conclusion(s)/implications

% Standard retrieval algorithms are known to fail over highly turbid Case 2 waters because they were developed specifically for the open ocean (Case 1 waters). 

% Standard atmospheric correction algorithms developed for heritage ocean color instruments (e.g. MODIS, SeaWiFS) require a sufficient SNR in two bands where the water-leaving signal is negligible, which is not always possible, particularly for Landsat 8's bands.

% Further atmospheric compensation technique based in algorithms currently used in Ocean Color sensors will be investigated.

% A LUT of spectral remote-sensing reflectances ($R_{rs}$) with different concentration of CPAs was produced using the in-water radiative transfer model Hydrolight. 


%
% Collections of water samples when the satellite passes over the Rochester area are planned for summer 2013, 2014 and 2015. 

% Concentration and inherent optical properties (IOPs) measurement will help to validate the methods.

\end{abstract}


% \chapter*{Acknowledgements}
% %*****************************************************************************************************
\begin{acknowledgements}
\phantomsection
\addcontentsline{toc}{chapter}{Acknowledgments}
\setlength{\parindent}{20pt}
I would like to extend special thanks to the United States Geological Survey (USGS) for its sponsorship (contract number G12PC00065) and for the free-access Landsat archive that has made this effort possible. Thanks to the Fulbright Commission for opening me the doors and sponsoring my M.S. degree. Special thanks to the Monroe County Environmental Laboratory of the Monroe County Department of Environmental Services for the $C_a$ and $TSS$ measurements used to validate our in-house concentration measurements, especially Scott, Providencia, and Gary. Nina Raque\~{n}o is thanked for her invaluable help in the logistic of the field data collections. Faculty, staff, and students at the Chester F. Carlson Center for Imaging Science at RIT for helping in the data collection, especially Paul Romanczyk, Rolando Raque\~{n}o, Aaron Gerace and Captain Mark. Thanks to the professors Dr. Kerekes, Dr. Messinger. Dr. Bachmann, and Dr. Vodacek, among others, for their support. Also, thanks to Dr. Christy Tyler for facilitating the Aquatic Ecology Lab at RIT for the $C_a$ measurements. Also, thanks to Ocean Color community, especially Dr. Emmanuel Boss and attendants of the 2013 Ocean color and instrumentation summer course at the Darling Marine Center for including me in their family. To my advisor Dr. John Schott for believing on me, guiding me and allowing me independence. Thanks to the administrative staff at the center, especially Cindy, Sue, and Amanda Zeluff for always helping me with a smile.

It is not easy to be far away from my beloved ones. I cannot describe the pride I feel of having what a supporting family that overcomes the sadness of not being together with the happiness of me achieving my goals. Thanks to my parents Osvaldo Concha Silva and Nelly del Carmen Sep\'ulveda Reyes for sacrificing their life for ours and always giving the best for our education. I would not be here if were not for them. Thanks to my siblings Loretto Constanza Concha Sep\'ulveda and Alvaro Nicol\'as Concha Sep\'ulveda for always supporting me.

Being at RIT and in Rochester, NY was a great experience. Many are the ones to thank for making my time here enjoyable. Especially thanks to my best support here in the U.S.: my dear friend Aixa de Jes\'us. My friends Aly, Anton, Claudia, Dmitry and my girlfriend Yana. To my classmates: Bikash, Viraj, Madurima, Peter Sun, Dave Kelbe, Leidy, and Gary. To the Latin Rhythm Dance Club at RIT, the Fulbright Scholars Association, and Tiger Tales Toastmansters International. My adopted Chilean family and dancers in Rochester: Marcia, Rosa and Doña Rosita, Raul, Willy and Marisol, Harold and Nancy. My Chilean friends in the University of Rochester: Felipe, Maria Eugenia, Emilio, Brenda, and Pauly. Finally, to the Rochester's dance community that helped me not to get insane on all these five years.
\end{acknowledgements}
%*****************************************************************************************************


\begin{dedication}
% \addcontentsline{toc}{chapter}{Dedication}

\centering
Dedicado a (Dedicated to):\\
\vspace{7cm}
Mis amados viejitos (My dear parents),\\ Osvaldo Concha Silva\\ y (and) \\ Nelly del Carmen Sep\'ulveda Reyes...

\end{dedication}


\tableofcontents
% \addcontentsline{toc}{chapter}{Contents}

\listoffigures
% \addcontentsline{toc}{chapter}{List of Figures}

\listoftables
% \addcontentsline{toc}{chapter}{List of Tables}


% \glsaddall

\printglossaries


% \addcontentsline{toc}{chapter}{Acronyms and Abbreviations}


% \input{Introduction.tex}

\include{Introduction}
\include{Objectives}
\include{Background_and_Theory}
\include{Methodology}
\include{Results}
\include{Summary}
\include{Appendix}


\printindex
\markboth{\it INDEX}{\it INDEX} % to change just this page header
\thispagestyle{fancy}

%\bibliographystyle{ieeetr}
%\bibliographystyle{unsrtnat}
% \addcontentsline{toc}{chapter}{Bibliography}
\bibliographystyle{apalike}
\bibliography{/Users/javier/Desktop/Javier/PHD_RIT/Latex/ThesisPhD/javier_bibPhD}

\include{Vita}

\listoftodos

\end{document}  